\section{Introduction}

A uses manager object manages a set of included (used) files.
In particular, the uses manager handles path lookups and
tracks what files have been opened.


\section{Interface}

\nwfilename{uses-manager.nw}\nwbegincode{1}\sublabel{NWuseF-useE-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-useE-1}}}\moddef{uses-manager.h~{\nwtagstyle{}\subpageref{NWuseF-useE-1}}}\endmoddef
#ifndef USES_MANAGER_H
#define USES_MANAGER_H

#include <stdio.h>
#include "mempool.h"

typedef struct uses_manager_struct* uses_manager_t;

\LA{}exported functions~{\nwtagstyle{}\subpageref{NWuseF-expI-1}}\RA{}

#endif /* USES_MANAGER_H */
\nwnotused{uses-manager.h}\nwendcode{}\nwbegindocs{2}\nwdocspar

A uses manager is allocated on a pool, which is where it will
keep its internal data structures.  There is no destructor
function -- to free the memory for a uses manager, you must
free the pool on which it was allocated.

\nwenddocs{}\nwbegincode{3}\sublabel{NWuseF-expI-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-expI-1}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NWuseF-expI-1}}}\endmoddef
uses_manager_t uses_manager_create(mempool_t pool);

\nwalsodefined{\\{NWuseF-expI-2}\\{NWuseF-expI-3}}\nwused{\\{NWuseF-useE-1}}\nwendcode{}\nwbegindocs{4}\nwdocspar

The uses manager keeps an internal list of paths for the purposes
of looking things up.  The {\tt{}uses{\char95}manager{\char95}addpath} function can
be used to \emph{prepend} to that list of paths.  There currently is no
function to \emph{append} to the list, and there probably
should be one, since order matters.  The current directory is
always implicitly the first thing on the path.  The {\tt{}uses{\char95}manager{\char95}envpath}
function includes a set of paths specified in the external environment.
The {\tt{}uses{\char95}manager{\char95}search} function searches its path for files
matching the name passed in {\tt{}namebuf}.
If it finds a match, {\tt{}namebuf} will be prepended with the appropriate
path and return a pointer to {\tt{}namebuf}.  If there is no match,
namebuf will be unmodified, and the function will return NULL.

\nwenddocs{}\nwbegincode{5}\sublabel{NWuseF-expI-2}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-expI-2}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NWuseF-expI-1}}}\plusendmoddef
void  uses_manager_addpath(uses_manager_t self, const char* path);
void  uses_manager_envpath(uses_manager_t self, const char* envname);
char* uses_manager_search (uses_manager_t self, char* namebuf, int buflen);

\nwendcode{}\nwbegindocs{6}\nwdocspar

We want to be able to register the files we use so that
we can get a list for later debugging, and so that we can
check whether a file has already been used.  The {\tt{}uses{\char95}manager{\char95}use}
function registers a file as used; the {\tt{}uses{\char95}manager{\char95}already{\char95}used}
function returns true iff a filename has already been entered via
{\tt{}uses{\char95}manager{\char95}use}.  The matching algorithm is not all that sophisticated,
so the same file accessed via different paths will be saved as two different
files.

\nwenddocs{}\nwbegincode{7}\sublabel{NWuseF-expI-3}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-expI-3}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NWuseF-expI-1}}}\plusendmoddef
void  uses_manager_use         (uses_manager_t self, const char* name);
int   uses_manager_already_used(uses_manager_t self, const char* name);
\nwendcode{}\nwbegindocs{8}\nwdocspar


\section{Implementation}

\nwenddocs{}\nwbegincode{9}\sublabel{NWuseF-useE.2-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-useE.2-1}}}\moddef{uses-manager.c~{\nwtagstyle{}\subpageref{NWuseF-useE.2-1}}}\endmoddef
#include <stdio.h>
#include <stdlib.h>
#include <string.h>
#include <string.h>

#include "uses-manager.h"

\LA{}types~{\nwtagstyle{}\subpageref{NWuseF-typ5-1}}\RA{}
\LA{}functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}\RA{}
\nwnotused{uses-manager.c}\nwendcode{}\nwbegindocs{10}\nwdocspar

A {\tt{}name{\char95}list{\char95}t} is just a linked list entry containing a pointer
to a path name (or file name).

\nwenddocs{}\nwbegincode{11}\sublabel{NWuseF-typ5-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-typ5-1}}}\moddef{types~{\nwtagstyle{}\subpageref{NWuseF-typ5-1}}}\endmoddef
typedef struct name_list_t \{
    const char* name;
    struct name_list_t* next;
\} name_list_t;

\nwalsodefined{\\{NWuseF-typ5-2}}\nwused{\\{NWuseF-useE.2-1}}\nwendcode{}\nwbegindocs{12}\nwdocspar

\nwenddocs{}\nwbegincode{13}\sublabel{NWuseF-typ5-2}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-typ5-2}}}\moddef{types~{\nwtagstyle{}\subpageref{NWuseF-typ5-1}}}\plusendmoddef
struct uses_manager_struct \{
    mempool_t pool;
    name_list_t* paths;
    name_list_t* files;    
\};

\nwendcode{}\nwbegindocs{14}\nwdocspar

Creating a uses manager is simple.  We just need to remember to store
a link to the pool for later allocations.

\nwenddocs{}\nwbegincode{15}\sublabel{NWuseF-fun9-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\endmoddef
uses_manager_t uses_manager_create(mempool_t pool)
\{
    uses_manager_t self = (uses_manager_t) 
        mempool_get(pool, sizeof(struct uses_manager_struct));

    self->pool = pool;
    self->paths = NULL;
    self->files = NULL;
    return self;
\}

\nwalsodefined{\\{NWuseF-fun9-2}\\{NWuseF-fun9-3}\\{NWuseF-fun9-4}\\{NWuseF-fun9-5}\\{NWuseF-fun9-6}\\{NWuseF-fun9-7}}\nwused{\\{NWuseF-useE.2-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar

When we add to the path, we \emph{prepend} by default.  The current
directory is always implicitly at the start of the path.

\nwenddocs{}\nwbegincode{17}\sublabel{NWuseF-fun9-2}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-fun9-2}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\plusendmoddef
void uses_manager_addpath(uses_manager_t self, const char* name)
\{
    name_list_t* link = (name_list_t*)
        mempool_get(self->pool, sizeof(struct name_list_t));

    link->name = mempool_strdup(self->pool, name);
    link->next = self->paths;
    self->paths = link;
\}

\nwendcode{}\nwbegindocs{18}\nwdocspar

\nwenddocs{}\nwbegincode{19}\sublabel{NWuseF-fun9-3}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-fun9-3}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\plusendmoddef
void uses_manager_envpath(uses_manager_t self, const char* envname)
\{
    char* names;
    char* name;

    if ((names = getenv(envname)) == NULL)
        return;

    names = mempool_strdup(self->pool, names);

    while ((name = strtok(names, ":")) != NULL) \{
        name_list_t* link = (name_list_t*)
            mempool_get(self->pool, sizeof(struct name_list_t));
        link->name = name;
        link->next = self->paths;
        self->paths = link;
        names = NULL;
    \}
\}

\nwendcode{}\nwbegindocs{20}\nwdocspar

If the world was POSIX compliant, I could use the {\tt{}access} function.
Alas, the world is not POSIX compliant.

\nwenddocs{}\nwbegincode{21}\sublabel{NWuseF-fun9-4}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-fun9-4}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\plusendmoddef
int uses_manager_access(const char* name)
\{
    FILE* fp = fopen(name, "r");
    if (fp) \{
        fclose(fp);
        return 0;
    \}
    return -1;
\}

\nwendcode{}\nwbegindocs{22}\nwdocspar

\nwenddocs{}\nwbegincode{23}\sublabel{NWuseF-fun9-5}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-fun9-5}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\plusendmoddef
char* uses_manager_search(uses_manager_t self, char* namebuf,
                          int buflen)
\{
    name_list_t* current_path = self->paths;

    \LA{}Check the current working directory~{\nwtagstyle{}\subpageref{NWuseF-CheZ-1}}\RA{}
    \LA{}Check all the paths in the list~{\nwtagstyle{}\subpageref{NWuseF-CheV-1}}\RA{}

    return NULL;
\}

\nwendcode{}\nwbegindocs{24}\nwdocspar

\nwenddocs{}\nwbegincode{25}\sublabel{NWuseF-CheZ-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-CheZ-1}}}\moddef{Check the current working directory~{\nwtagstyle{}\subpageref{NWuseF-CheZ-1}}}\endmoddef
if (uses_manager_access(namebuf) == 0)
    return namebuf;
\nwused{\\{NWuseF-fun9-5}}\nwendcode{}\nwbegindocs{26}\nwdocspar

Note that {\tt{}tmpbuf} has two characters extra space for the end-of-string
and for a path separator character.

\nwenddocs{}\nwbegincode{27}\sublabel{NWuseF-CheV-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-CheV-1}}}\moddef{Check all the paths in the list~{\nwtagstyle{}\subpageref{NWuseF-CheV-1}}}\endmoddef
while (current_path != NULL) \{

    int tmpbuflen = strlen(current_path->name) +
                    strlen(namebuf) + 2;
    char* tmpbuf = (char*) mempool_geth(self->pool, tmpbuflen);

    \LA{}Build path name~{\nwtagstyle{}\subpageref{NWuseF-BuiF-1}}\RA{}
    if (uses_manager_access(tmpbuf) == 0) \{
        \LA{}Copy result to namebuf and return~{\nwtagstyle{}\subpageref{NWuseF-CopX-1}}\RA{}
    \}
    
    mempool_freeh(tmpbuf);
    current_path = current_path->next;
\}
\nwused{\\{NWuseF-fun9-5}}\nwendcode{}\nwbegindocs{28}\nwdocspar

There should probably be something to handle platform-specific
path component separator characters, too.

\nwenddocs{}\nwbegincode{29}\sublabel{NWuseF-BuiF-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-BuiF-1}}}\moddef{Build path name~{\nwtagstyle{}\subpageref{NWuseF-BuiF-1}}}\endmoddef
strcpy(tmpbuf, current_path->name);
strcat(tmpbuf, "/");
strcat(tmpbuf, namebuf);
\nwused{\\{NWuseF-CheV-1}}\nwendcode{}\nwbegindocs{30}\nwdocspar

Note that if the buffer isn't large enough, we return NULL.
This perhaps isn't ideal, but returning the truncated file name
seems evil.

\nwenddocs{}\nwbegincode{31}\sublabel{NWuseF-CopX-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-CopX-1}}}\moddef{Copy result to namebuf and return~{\nwtagstyle{}\subpageref{NWuseF-CopX-1}}}\endmoddef
if (strlen(tmpbuf) + 1 > buflen) \{
    mempool_freeh(tmpbuf);
    return NULL;
\} else \{
    strcpy(namebuf, tmpbuf);
    mempool_freeh(tmpbuf);
    return namebuf;
\}
\nwused{\\{NWuseF-CheV-1}}\nwendcode{}\nwbegindocs{32}\nwdocspar

Saving a name in the ``used'' list and checking whether a name
is in the use list are just basic linked list operations.
This is \emph{not} a particularly time-efficient implementation.
Something more sophisticated might use a hash table.

\nwenddocs{}\nwbegincode{33}\sublabel{NWuseF-fun9-6}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-fun9-6}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\plusendmoddef
void uses_manager_use(uses_manager_t self, const char* name)
\{
    if (!uses_manager_already_used(self, name)) \{
        name_list_t* new_link = (name_list_t*)
            mempool_get(self->pool, sizeof(name_list_t));

        new_link->name = mempool_strdup(self->pool, name);
        new_link->next = self->files;
        self->files = new_link;
    \}
\}

\nwendcode{}\nwbegindocs{34}\nwdocspar

\nwenddocs{}\nwbegincode{35}\sublabel{NWuseF-fun9-7}\nwmargintag{{\nwtagstyle{}\subpageref{NWuseF-fun9-7}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWuseF-fun9-1}}}\plusendmoddef
int uses_manager_already_used(uses_manager_t self, const char* name)
\{
    name_list_t* link = self->files;
    while (link != NULL) \{
        if (strcmp(link->name, name) == 0)
            return 1;
        link = link->next;
    \}
    return 0;
\}

\nwendcode{}

\nwixlogsorted{c}{{Build path name}{NWuseF-BuiF-1}{\nwixu{NWuseF-CheV-1}\nwixd{NWuseF-BuiF-1}}}%
\nwixlogsorted{c}{{Check all the paths in the list}{NWuseF-CheV-1}{\nwixu{NWuseF-fun9-5}\nwixd{NWuseF-CheV-1}}}%
\nwixlogsorted{c}{{Check the current working directory}{NWuseF-CheZ-1}{\nwixu{NWuseF-fun9-5}\nwixd{NWuseF-CheZ-1}}}%
\nwixlogsorted{c}{{Copy result to namebuf and return}{NWuseF-CopX-1}{\nwixu{NWuseF-CheV-1}\nwixd{NWuseF-CopX-1}}}%
\nwixlogsorted{c}{{exported functions}{NWuseF-expI-1}{\nwixu{NWuseF-useE-1}\nwixd{NWuseF-expI-1}\nwixd{NWuseF-expI-2}\nwixd{NWuseF-expI-3}}}%
\nwixlogsorted{c}{{functions}{NWuseF-fun9-1}{\nwixu{NWuseF-useE.2-1}\nwixd{NWuseF-fun9-1}\nwixd{NWuseF-fun9-2}\nwixd{NWuseF-fun9-3}\nwixd{NWuseF-fun9-4}\nwixd{NWuseF-fun9-5}\nwixd{NWuseF-fun9-6}\nwixd{NWuseF-fun9-7}}}%
\nwixlogsorted{c}{{types}{NWuseF-typ5-1}{\nwixu{NWuseF-useE.2-1}\nwixd{NWuseF-typ5-1}\nwixd{NWuseF-typ5-2}}}%
\nwixlogsorted{c}{{uses-manager.c}{NWuseF-useE.2-1}{\nwixd{NWuseF-useE.2-1}}}%
\nwixlogsorted{c}{{uses-manager.h}{NWuseF-useE-1}{\nwixd{NWuseF-useE-1}}}%
\nwbegindocs{36}\nwdocspar

\nwenddocs{}
