% ===> this file was generated automatically by noweave --- better not edit it
\section{Introduction}

The purpose of the matrix assembly module is to build global matrix 
and vector data structures from local contributions.  But what sort of global
matrices should we build?  We might want a dense matrix, or any of
a variety of sparse formats.  There might be a reordering in effect,
or there might not.  We might throw away inactive degrees of freedom,
or we might not.

Since there are a variety of possible data structures we might want
to build, we make a generic matrix assembler type.  Given a list of
variable identifiers and a local contribution (a dense vector if we
are building a vector, and a dense column-major matrix if we are
building matrices), the assemble method incorporates the local contribution
into the global structure.  Information can flow the other way as well --
using the same interface, we can construct ``disassembler'' objects that
extract the local part from global structures.


\section{Interface}

\nwfilename{assemblem.nw}\nwbegincode{1}\sublabel{NW3qDCht-3YiIiA-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3qDCht-3YiIiA-1}}}\moddef{assemblem.h~{\nwtagstyle{}\subpageref{NW3qDCht-3YiIiA-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
#ifndef ASSEMBLEM_H
#define ASSEMBLEM_H

\LA{}exported types~{\nwtagstyle{}\subpageref{NW3qDCht-4aCyDR-1}}\RA{}
\LA{}exported functions~{\nwtagstyle{}\subpageref{NW3qDCht-2gXoUc-1}}\RA{}

#endif /* ASSEMBLEM_H */
\nwnotused{assemblem.h}\nwendcode{}\nwbegindocs{2}\nwdocspar

\nwenddocs{}\nwbegincode{3}\sublabel{NW3qDCht-4aCyDR-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3qDCht-4aCyDR-1}}}\moddef{exported types~{\nwtagstyle{}\subpageref{NW3qDCht-4aCyDR-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3qDCht-3YiIiA-1}}\nwenddeflinemarkup
typedef void (*assemble_matrix_fun_t)(void* self, int* vars, int n, 
                                      double* local);

typedef struct assemble_matrix_t \{
    void*   data;
    void  (*assemble)(void* self, int* vars, int n, double* local);
    void  (*destroy) (void* self);
\} assemble_matrix_t;

\nwused{\\{NW3qDCht-3YiIiA-1}}\nwendcode{}\nwbegindocs{4}\nwdocspar

The {\Tt{}assemble{\_}matrix{\_}t\nwendquote} object interface is the main type
exported by this module.  The {\Tt{}assemble\nwendquote} method
moves a local contribution into the global data structure
maintained by the object.  The {\Tt{}vars\nwendquote} argument is a vector
of {\Tt{}n\nwendquote} variable indices that identify the global location
of the local contributions.  The {\Tt{}local\nwendquote} field contains
the contribution itself.  If the assembler object is building
matrices, the {\Tt{}local\nwendquote} field should point to an {\Tt{}n\nwendquote} by {\Tt{}n\nwendquote}
matrix in column major order.  If the assembler object builds
vectors, the {\Tt{}local\nwendquote} field should point to a vector of length
{\Tt{}n\nwendquote}.

The {\Tt{}destroy\nwendquote} method performs any deallocation of the object
local data.  The {\Tt{}destroy\nwendquote} method does not free the data pointed
to by {\Tt{}data\nwendquote} by default.

\nwenddocs{}\nwbegincode{5}\sublabel{NW3qDCht-2gXoUc-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3qDCht-2gXoUc-1}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NW3qDCht-2gXoUc-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3qDCht-3YiIiA-1}}\nwprevnextdefs{\relax}{NW3qDCht-2gXoUc-2}\nwenddeflinemarkup
void assemble_matrix_add(assemble_matrix_t* matrix, int* vars, int n, 
                                 double* local);
void assemble_matrix_add1(assemble_matrix_t* matrix, int var, 
                                  double local);

\nwalsodefined{\\{NW3qDCht-2gXoUc-2}}\nwused{\\{NW3qDCht-3YiIiA-1}}\nwendcode{}\nwbegindocs{6}\nwdocspar

The {\Tt{}assemble{\_}matrix{\_}add\nwendquote} function is just a convenient wrapper
to call the assemble method.  The {\Tt{}assemble{\_}matrix{\_}add1\nwendquote} function
adds a single entry to a vector or matrix.

\nwenddocs{}\nwbegincode{7}\sublabel{NW3qDCht-2gXoUc-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW3qDCht-2gXoUc-2}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NW3qDCht-2gXoUc-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3qDCht-3YiIiA-1}}\nwprevnextdefs{NW3qDCht-2gXoUc-1}{\relax}\nwenddeflinemarkup
void assembler_matrix_free(assemble_matrix_t* assembler);
\nwused{\\{NW3qDCht-3YiIiA-1}}\nwendcode{}\nwbegindocs{8}\nwdocspar

The destructor {\Tt{}assembler{\_}matrix{\_}free\nwendquote} calls the assembler
object {\Tt{}destroy\nwendquote} method (if such a method is defined),
and then frees the {\Tt{}assemble{\_}matrix{\_}t\nwendquote} structure.


\section{Implementation}

\nwenddocs{}\nwbegincode{9}\sublabel{NW3qDCht-1WXbOU-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3qDCht-1WXbOU-1}}}\moddef{assemblem.c~{\nwtagstyle{}\subpageref{NW3qDCht-1WXbOU-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
#include <sugar.h>

#include <stdlib.h>
#include <string.h>
#include <assert.h>

#include <modelmgr.h>
#include <assemblem.h>

\LA{}functions~{\nwtagstyle{}\subpageref{NW3qDCht-nRuDO-1}}\RA{}
\nwnotused{assemblem.c}\nwendcode{}\nwbegindocs{10}\nwdocspar

\nwenddocs{}\nwbegincode{11}\sublabel{NW3qDCht-nRuDO-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3qDCht-nRuDO-1}}}\moddef{functions~{\nwtagstyle{}\subpageref{NW3qDCht-nRuDO-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3qDCht-1WXbOU-1}}\nwenddeflinemarkup
void assemble_matrix_add(assemble_matrix_t* matrix, int* vars, int n, 
                                 double* local)
\{
    assert(matrix != NULL && matrix->assemble != NULL);
    matrix->assemble(matrix->data, vars, n, local);
\}

void assemble_matrix_add1(assemble_matrix_t* matrix, int var,
                                  double local)
\{
    assemble_matrix_add(matrix, &var, 1, &local);
\}

void assembler_matrix_free(assemble_matrix_t* matrix)
\{
    assert(matrix != NULL);
    if (matrix->destroy)
        matrix->destroy(matrix->data);
    free(matrix);
\}

\nwused{\\{NW3qDCht-1WXbOU-1}}\nwendcode{}

\nwixlogsorted{c}{{assemblem.c}{NW3qDCht-1WXbOU-1}{\nwixd{NW3qDCht-1WXbOU-1}}}%
\nwixlogsorted{c}{{assemblem.h}{NW3qDCht-3YiIiA-1}{\nwixd{NW3qDCht-3YiIiA-1}}}%
\nwixlogsorted{c}{{exported functions}{NW3qDCht-2gXoUc-1}{\nwixu{NW3qDCht-3YiIiA-1}\nwixd{NW3qDCht-2gXoUc-1}\nwixd{NW3qDCht-2gXoUc-2}}}%
\nwixlogsorted{c}{{exported types}{NW3qDCht-4aCyDR-1}{\nwixu{NW3qDCht-3YiIiA-1}\nwixd{NW3qDCht-4aCyDR-1}}}%
\nwixlogsorted{c}{{functions}{NW3qDCht-nRuDO-1}{\nwixu{NW3qDCht-1WXbOU-1}\nwixd{NW3qDCht-nRuDO-1}}}%
\nwbegindocs{12}\nwdocspar
\nwenddocs{}
