% ===> this file was generated automatically by noweave --- better not edit it
\section{Introduction}

The {\Tt{}mex{\_}handle\nwendquote} module keeps track of C data structures by numeric
handles, so that Matlab users can refer to C objects by providing a
handle.


\section{Interface}

\nwfilename{mex-handle.nw}\nwbegincode{1}\sublabel{NWNhLk6-4fAjjr-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-4fAjjr-1}}}\moddef{mex-handle.h~{\nwtagstyle{}\subpageref{NWNhLk6-4fAjjr-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
#ifndef MEX_HANDLE_H
#define MEX_HANDLE_H

\LA{}exported functions~{\nwtagstyle{}\subpageref{NWNhLk6-2gXoUc-1}}\RA{}

#endif /* MEX_HANDLE_H */
\nwnotused{mex-handle.h}\nwendcode{}\nwbegindocs{2}\nwdocspar

The handle manager object is a statically-allocated singleton.
It is initialized by {\Tt{}create\nwendquote} and destroyed by {\Tt{}destroy\nwendquote}.

\nwenddocs{}\nwbegincode{3}\sublabel{NWNhLk6-2gXoUc-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-2gXoUc-1}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NWNhLk6-2gXoUc-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-4fAjjr-1}}\nwprevnextdefs{\relax}{NWNhLk6-2gXoUc-2}\nwenddeflinemarkup
void mex_handle_create ();
void mex_handle_destroy();

\nwalsodefined{\\{NWNhLk6-2gXoUc-2}\\{NWNhLk6-2gXoUc-3}}\nwused{\\{NWNhLk6-4fAjjr-1}}\nwendcode{}\nwbegindocs{4}\nwdocspar

Each object stored by the handle manager has a data field
and a numeric type tag.  New tags can be allocated using
the {\Tt{}new{\_}tag\nwendquote} routine.  The zero tag is reserved for empty
handle slots.

\nwenddocs{}\nwbegincode{5}\sublabel{NWNhLk6-2gXoUc-2}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-2gXoUc-2}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NWNhLk6-2gXoUc-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-4fAjjr-1}}\nwprevnextdefs{NWNhLk6-2gXoUc-1}{NWNhLk6-2gXoUc-3}\nwenddeflinemarkup
int   mex_handle_new_tag();

\nwused{\\{NWNhLk6-4fAjjr-1}}\nwendcode{}\nwbegindocs{6}\nwdocspar

The {\Tt{}add\nwendquote} function allocates a new handle.  The {\Tt{}find\nwendquote}
function locates a handle that has already been allocated.
Once a handle has been allocated, the associated data and tag fields can
be retrieved with the {\Tt{}data\nwendquote} and {\Tt{}tag\nwendquote} methods.  If
the handle is not valid, {\Tt{}data\nwendquote} will return NULL and {\Tt{}tag\nwendquote}
will return zero.  The {\Tt{}remove\nwendquote} function deallocates a handle;
future references to that handle will be invalid.

\nwenddocs{}\nwbegincode{7}\sublabel{NWNhLk6-2gXoUc-3}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-2gXoUc-3}}}\moddef{exported functions~{\nwtagstyle{}\subpageref{NWNhLk6-2gXoUc-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-4fAjjr-1}}\nwprevnextdefs{NWNhLk6-2gXoUc-2}{\relax}\nwenddeflinemarkup
int   mex_handle_add   (void* data, int tag);
int   mex_handle_find  (void* data, int tag);
int   mex_handle_tag   (int handle_id);
void* mex_handle_data  (int handle_id);
void* mex_handle_remove(int handle_id);

\nwused{\\{NWNhLk6-4fAjjr-1}}\nwendcode{}\nwbegindocs{8}\nwdocspar

\section{Implementation}

\nwenddocs{}\nwbegincode{9}\sublabel{NWNhLk6-22fNlv-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-22fNlv-1}}}\moddef{mex-handle.c~{\nwtagstyle{}\subpageref{NWNhLk6-22fNlv-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
#include <sugar.h>

#include <stdio.h>

#include <mex_handle.h>
#include <dynarray.h>

typedef struct mex_handle_t \{
    void* data;
    int   tag;
    int   id;
\} mex_handle_t;

static dynarray_t handles;
static int next_tag;
static int next_id;
static int free_list;

\LA{}functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}\RA{}
\nwnotused{mex-handle.c}\nwendcode{}\nwbegindocs{10}\nwdocspar

The handles are stored in the dynamic array {\Tt{}handles\nwendquote}.  Each handle
has a data pointer, a tag, and a field for the handle identifier.
The {\Tt{}next{\_}tag\nwendquote} and {\Tt{}next{\_}id\nwendquote} variables keep track of the number
of tags and handle identifiers that have been allocated over the lifetime
of the handle manager.

\nwenddocs{}\nwbegincode{11}\sublabel{NWNhLk6-nRuDO-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-22fNlv-1}}\nwprevnextdefs{\relax}{NWNhLk6-nRuDO-2}\nwenddeflinemarkup
void mex_handle_create()
\{
    handles   = dynarray_create(sizeof(mex_handle_t), 16);
    next_tag  = 1;
    next_id   = 1;
    free_list = -1;
\}

void mex_handle_destroy()
\{
    dynarray_destroy(handles);
\}

\nwalsodefined{\\{NWNhLk6-nRuDO-2}\\{NWNhLk6-nRuDO-3}\\{NWNhLk6-nRuDO-4}\\{NWNhLk6-nRuDO-5}\\{NWNhLk6-nRuDO-6}\\{NWNhLk6-nRuDO-7}}\nwused{\\{NWNhLk6-22fNlv-1}}\nwendcode{}\nwbegindocs{12}\nwdocspar

Allocating a new tag is just a matter of incrementing the {\Tt{}next{\_}tag\nwendquote} flag.

\nwenddocs{}\nwbegincode{13}\sublabel{NWNhLk6-nRuDO-2}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-2}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-22fNlv-1}}\nwprevnextdefs{NWNhLk6-nRuDO-1}{NWNhLk6-nRuDO-3}\nwenddeflinemarkup
int mex_handle_new_tag()
\{
    return next_tag++;
\}

\nwused{\\{NWNhLk6-22fNlv-1}}\nwendcode{}\nwbegindocs{14}\nwdocspar

At a high level, the {\Tt{}add\nwendquote} and {\Tt{}remove\nwendquote} operations are simple, too.
To add a handle, we need only to find a space for it, set the fields,
and assign an identifier.  To remove a handle, we grab the handle data,
deallocate the handle, and return the data pointer.

\nwenddocs{}\nwbegincode{15}\sublabel{NWNhLk6-nRuDO-3}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-3}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-22fNlv-1}}\nwprevnextdefs{NWNhLk6-nRuDO-2}{NWNhLk6-nRuDO-4}\nwenddeflinemarkup
int mex_handle_add(void* data, int tag)
\{
    int index;
    mex_handle_t* handle;

    \LA{}allocate handle~{\nwtagstyle{}\subpageref{NWNhLk6-109qp6-1}}\RA{}
    handle->data = data;
    handle->tag  = tag;
    handle->id   = \LA{}allocate handle identifier~{\nwtagstyle{}\subpageref{NWNhLk6-48sA3f-1}}\RA{}

    return handle->id;
\}

\nwused{\\{NWNhLk6-22fNlv-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar

\nwenddocs{}\nwbegincode{17}\sublabel{NWNhLk6-nRuDO-4}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-4}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-22fNlv-1}}\nwprevnextdefs{NWNhLk6-nRuDO-3}{NWNhLk6-nRuDO-5}\nwenddeflinemarkup
void* mex_handle_remove(int handle_id)
\{
    int index;
    mex_handle_t* handle;
    void*         data;

    \LA{}find handle identifier~{\nwtagstyle{}\subpageref{NWNhLk6-kHjXn-1}}\RA{}

    if (handle == NULL)
        return NULL;
    else \{
        data = handle->data;
        \LA{}deallocate handle~{\nwtagstyle{}\subpageref{NWNhLk6-1mZPrH-1}}\RA{}
        return data;
    \}
\}

\nwused{\\{NWNhLk6-22fNlv-1}}\nwendcode{}\nwbegindocs{18}\nwdocspar

The {\Tt{}find\nwendquote} function returns the identifier for a handle that has
already been allocated.

\nwenddocs{}\nwbegincode{19}\sublabel{NWNhLk6-nRuDO-5}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-5}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-22fNlv-1}}\nwprevnextdefs{NWNhLk6-nRuDO-4}{NWNhLk6-nRuDO-6}\nwenddeflinemarkup
int mex_handle_find(void* data, int tag)
\{
    int i, n;
    mex_handle_t* handle_data = dynarray_data(handles);

    n = dynarray_count(handles);
    for (i = 0; i < n; ++i) \{
        if (handle_data[i].tag == tag && handle_data[i].data == data)
            return handle_data[i].id;
    \}
    return 0;
\}

\nwused{\\{NWNhLk6-22fNlv-1}}\nwendcode{}\nwbegindocs{20}\nwdocspar

The {\Tt{}tag\nwendquote} and {\Tt{}data\nwendquote} functions find a handle and return its data
field (or zero if the handle is invalid).

\nwenddocs{}\nwbegincode{21}\sublabel{NWNhLk6-nRuDO-6}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-6}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-22fNlv-1}}\nwprevnextdefs{NWNhLk6-nRuDO-5}{NWNhLk6-nRuDO-7}\nwenddeflinemarkup
int mex_handle_tag(int handle_id)
\{
    int index;
    mex_handle_t* handle;

    \LA{}find handle identifier~{\nwtagstyle{}\subpageref{NWNhLk6-kHjXn-1}}\RA{}

    return (handle != NULL) ? handle->tag : 0;
\}

\nwused{\\{NWNhLk6-22fNlv-1}}\nwendcode{}\nwbegindocs{22}\nwdocspar

\nwenddocs{}\nwbegincode{23}\sublabel{NWNhLk6-nRuDO-7}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-7}}}\moddef{functions~{\nwtagstyle{}\subpageref{NWNhLk6-nRuDO-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-22fNlv-1}}\nwprevnextdefs{NWNhLk6-nRuDO-6}{\relax}\nwenddeflinemarkup
void* mex_handle_data(int handle_id)
\{
    int index;
    mex_handle_t* handle;

    \LA{}find handle identifier~{\nwtagstyle{}\subpageref{NWNhLk6-kHjXn-1}}\RA{}

    return (handle != NULL) ? handle->data : NULL;
\}

\nwused{\\{NWNhLk6-22fNlv-1}}\nwendcode{}\nwbegindocs{24}\nwdocspar

We keep a free list of deallocated handle slots for re-use, since
it seems likely that they will be deallocated pretty often.
The handle {\Tt{}id\nwendquote} field is used to point to the next slot on
the free list, and $-1$ serves the role of a NULL.  If we want
a new slot and there are none available from the free list, we
just expand the array to accomodate a new handle.

\nwenddocs{}\nwbegincode{25}\sublabel{NWNhLk6-109qp6-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-109qp6-1}}}\moddef{allocate handle~{\nwtagstyle{}\subpageref{NWNhLk6-109qp6-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-nRuDO-3}}\nwenddeflinemarkup
if (free_list >= 0) \{
    index      = free_list;
    handle     = dynarray_get(handles, index);
    free_list  = handle->id;
\} else \{
    index      = dynarray_count(handles);
    handle     = dynarray_append(handles, NULL);
\}

\nwused{\\{NWNhLk6-nRuDO-3}}\nwendcode{}\nwbegindocs{26}\nwdocspar

\nwenddocs{}\nwbegincode{27}\sublabel{NWNhLk6-1mZPrH-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-1mZPrH-1}}}\moddef{deallocate handle~{\nwtagstyle{}\subpageref{NWNhLk6-1mZPrH-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-nRuDO-4}}\nwenddeflinemarkup
handle->tag  = 0;
handle->data = NULL;
handle->id   = free_list;
free_list    = index;

\nwused{\\{NWNhLk6-nRuDO-4}}\nwendcode{}\nwbegindocs{28}\nwdocspar

A natural way to pick handle identifiers would be to use the
array index of the identifier.  There is a problem
with this approach, though.  We would like small,
common numbers like $0$ and $1$ \emph{not} to be valid handles.
It makes it more difficult for the user to accidentally retrieve 
a valid handle that was not returned to him.  Similarly, we would
like the handles not to be too close together, so that taking a
valid handle and adding one to it doesn't yield another valid handle.

We can get a more scattered space of handles by putting some unique
identifying information in the high order bits and using the low
order bits for index information.  For the moment, we'll use the
lower ten bits for indexing.  I doubt we'll ever have more than 256
simultaneously active handles, so the for loop used to retrieve
the handle identifiers will probably never go past the first iteration
unless there is an error.

\nwenddocs{}\nwbegincode{29}\sublabel{NWNhLk6-48sA3f-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-48sA3f-1}}}\moddef{allocate handle identifier~{\nwtagstyle{}\subpageref{NWNhLk6-48sA3f-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-nRuDO-3}}\nwenddeflinemarkup
(next_tag++ << 8) + (index & 255);
\nwused{\\{NWNhLk6-nRuDO-3}}\nwendcode{}\nwbegindocs{30}\nwdocspar

\nwenddocs{}\nwbegincode{31}\sublabel{NWNhLk6-kHjXn-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWNhLk6-kHjXn-1}}}\moddef{find handle identifier~{\nwtagstyle{}\subpageref{NWNhLk6-kHjXn-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWNhLk6-nRuDO-4}\\{NWNhLk6-nRuDO-6}\\{NWNhLk6-nRuDO-7}}\nwenddeflinemarkup
for (index = (handle_id & 255);
     (handle = dynarray_get(handles, index)) != NULL &&
         handle->id != handle_id;
     index += 256);
\nwused{\\{NWNhLk6-nRuDO-4}\\{NWNhLk6-nRuDO-6}\\{NWNhLk6-nRuDO-7}}\nwendcode{}

\nwixlogsorted{c}{{allocate handle}{NWNhLk6-109qp6-1}{\nwixu{NWNhLk6-nRuDO-3}\nwixd{NWNhLk6-109qp6-1}}}%
\nwixlogsorted{c}{{allocate handle identifier}{NWNhLk6-48sA3f-1}{\nwixu{NWNhLk6-nRuDO-3}\nwixd{NWNhLk6-48sA3f-1}}}%
\nwixlogsorted{c}{{deallocate handle}{NWNhLk6-1mZPrH-1}{\nwixu{NWNhLk6-nRuDO-4}\nwixd{NWNhLk6-1mZPrH-1}}}%
\nwixlogsorted{c}{{exported functions}{NWNhLk6-2gXoUc-1}{\nwixu{NWNhLk6-4fAjjr-1}\nwixd{NWNhLk6-2gXoUc-1}\nwixd{NWNhLk6-2gXoUc-2}\nwixd{NWNhLk6-2gXoUc-3}}}%
\nwixlogsorted{c}{{find handle identifier}{NWNhLk6-kHjXn-1}{\nwixu{NWNhLk6-nRuDO-4}\nwixu{NWNhLk6-nRuDO-6}\nwixu{NWNhLk6-nRuDO-7}\nwixd{NWNhLk6-kHjXn-1}}}%
\nwixlogsorted{c}{{functions}{NWNhLk6-nRuDO-1}{\nwixu{NWNhLk6-22fNlv-1}\nwixd{NWNhLk6-nRuDO-1}\nwixd{NWNhLk6-nRuDO-2}\nwixd{NWNhLk6-nRuDO-3}\nwixd{NWNhLk6-nRuDO-4}\nwixd{NWNhLk6-nRuDO-5}\nwixd{NWNhLk6-nRuDO-6}\nwixd{NWNhLk6-nRuDO-7}}}%
\nwixlogsorted{c}{{mex-handle.c}{NWNhLk6-22fNlv-1}{\nwixd{NWNhLk6-22fNlv-1}}}%
\nwixlogsorted{c}{{mex-handle.h}{NWNhLk6-4fAjjr-1}{\nwixd{NWNhLk6-4fAjjr-1}}}%
\nwbegindocs{32}\nwdocspar

\nwenddocs{}
